\documentclass[11pt,parskip]{beamer}
\input{PreambleSlides}
\usetheme{CambridgeUS}
\usecolortheme{rose}
\title[]{Invariant Geometric Structures and \\ Chern numbers of  $G_2$ Flag Manifolds}
\author[]{Dani\"el Thung}
\institute[]{LMU Munich}
\date{}

\begin{document}

\begin{frame}[plain]
\maketitle
\end{frame}

\begin{frame}{Outline}
	\begin{enumerate}
		\item Generalized flag manifolds
		\bigskip
		\item Flag manifolds of $G_2$
		\bigskip
		\item The twistor space
		\bigskip
		\item The quadric
	\end{enumerate}
\end{frame}

\begin{frame}{Generalized flag manifolds}
	\begin{mydef}
		A \emph{flag} is an increasing sequence 
		\begin{equation*}
			\{0\}=V_0\subset V_1 \subset V_2 \subset \dots \subset V_k=V \qquad \qquad k\leq n
		\end{equation*}
		of subspaces of an $n$-dimensional vector space $V$ (e.g.~$\R^n$ or $\C^n$). Set $d_i=\dim V_i$; then $(d_1,\dots, d_{k-1})$ is the signature of the flag. If $d_i=i$, we call the flag \emph{complete} and otherwise we have a \emph{partial} flag. 
	\end{mydef}	
\end{frame}
\begin{frame}{Generalized flag manifolds}
	\begin{ex}[Flag manifolds of flags in $\C^n$]
		\begin{letteredlist}
			\item The Grassmannian of $k$-planes parametrizes flags of signature $(k)$:
			\begin{equation*}
				\Gr_k(\C^n)\cong \frac{U(n)}{U(k)\times U(n-k)}
			\end{equation*}\pause
			\item The manifold of \emph{complete} flags is $U(n)/T^n$.\pause
			\item In general, any \emph{flag manifold} of flags in $\C^n$ is of the form
			\begin{equation*}
				\frac{U(n)}{U(r_1)\times\dots U(r_k)}
			\end{equation*}
			where $\{r_1,\dots,r_k\}$ is an ordered partition of $n$. The isotropy subgroup is the centralizer of a torus $T^k$.
		\end{letteredlist}
	\end{ex}
\end{frame}
\begin{frame}{Generalized flag manifolds}
	\begin{mydef}
		A \emph{generalized flag manifold} is a homogeneous space of the form $G/C(T)$, where $G$ is a compact, connected and semisimple Lie group, and $C(T)$ is the centralizer of a torus $T\subset G$.
	\end{mydef}
	Generalized flag manifolds carry interesting $G$-invariant structures:\pause
	
	\begin{thm}[Borel~\cite{Bor1953}, Koszul~\cite{Kos1955}]
		Every generalized flag manifold admits a unique (up to scaling) K\"ahler-Einstein metric; it has positive scalar curvature.
	\end{thm}\pause
	
	Furthermore, generalized flag manifolds often carry multiple invariant almost complex structures with distinct Chern numbers (Borel \& Hirzebruch~\cite{BH1958}).
\end{frame}

\begin{frame}[fragile]{$G_2$ flag manifolds}
	The exceptional Lie group $G_2$ is the automorphism group of the octonions $\O$. Its generalized flag manifolds fit into the following diagram: \pause
	\begin{figure}\centering
		\begin{tikzpicture}
			\draw (3,3) node{$G_2/T^2$};\pause
			\draw (1,1.5) node{\color{red}{$G_2/U(2)_-$}};
			\draw[->] (2.5,2.75) -- (1.5,2)
				node[pos=0.5, anchor=south east]{\footnotesize{$\CP^1$}};\pause
			\draw (-1.2,0) node{$G_2/SU(3)\cong S^6$};
			\draw[->] (0.3,1.2) -- (-0.7,0.5)
				node[pos=0.5, anchor=south east]{\footnotesize{$\CP^2$}};\pause
			\draw[->] (3.35,2.75) -- (4.5,2)
				node[pos=0.5, anchor=south west]{\footnotesize{$\CP^1$}};
			\draw (5.15,1.5) node{\color{red}{$G_2/U(2)_+$}};\pause
			\draw[->] (1.7,1.2) -- (2.7,0.5)
				node[pos=0.5, anchor=north east]{\footnotesize{$\CP^1$}};
			\draw[->] (4.45,1.2) -- (3.45,0.5)
				node[pos=0.5, anchor=north west]{\footnotesize{$\CP^1$}};
			\draw (3.075,0) node{$G_2/SO(4)$};\pause
			\draw (2.25,1.55) node{\color{red}{$=Q$}};
			\draw (6.35,1.55) node{\color{red}{$=Z$}};
		\end{tikzpicture}
	\end{figure}
\end{frame}

\begin{frame}{The twistor space}
	$\pi:Z\to G_2/SO(4)$ exhibits $Z$ as the \emph{twistor space} over $G_2/SO(4)$, which is a quaternionic K\"ahler manifold. \pause
	
	\bigskip
	
	\begin{mydef}
		A quaternionic K\"ahler (QK) manifold is an (oriented) Riemannian manifold of dimension $4n$, $n\geq 2$, whose holonomy group is contained in the subgroup $Sp(n)\cdot Sp(1)$ of $SO(4n)$.
	\end{mydef}\pause

	\bigskip

	QK manifolds are Einstein, but not necessarily Ricci-flat. 
\end{frame}

\begin{frame}{The twistor space}
	Any QK manifold $M$ carries a rank 3 subbundle $H$ of $\End TM$, locally spanned by a quaternionic triple $\{I,J,IJ=K\}$.\pause
	
	\medskip
	
	\begin{mydef}[Salamon~\cite{Sal1982}]
		The total space $Y$ of the sphere bundle of $H$ is called the \emph{twistor space} over $M$.
	\end{mydef}\pause

	\medskip
	
	\begin{thm}[Salamon~\cite{Sal1982}, B\'erard-Bergery~\cite{Bes2008}]
		\begin{numberedlist}
			\item $Y$ admits a natural (integrable) complex structure.
			\item If $M$ has positive scalar curvature, then $Y$ admits a K\"ahler-Einstein metric with positive scalar curvature.
		\end{numberedlist}
	\end{thm}	
\end{frame}

\begin{frame}{The twistor space: Rigidity of the K\"ahler structure}
	Using the Gysin sequence we determine the cohomology ring and Pontryagin classes of $Z=G_2/U(2)_+$. Additively, the cohomology is that of $\CP^5$, but not multiplicatively.\pause
	
	\bigskip 
	
	\begin{thm}
		Let $X$ be a K\"ahler manifold. If it is homeomorphic to $Z$, then it is biholomorphic to $Z$
	\end{thm}\pause
	
	\bigskip
	
	This is the analog of rigidity results of Hirzebruch \& Kodaira~\cite{HK1957} (and Yau~\cite{Yau1977}) for $\CP^n$, and Brieskorn~\cite{Bri1964} for $Q_n$ ($n\geq 3$).
\end{frame}



\begin{frame}{The twistor space: Rigidity of the K\"ahler structure}
	\begin{myproof}[Sketch of Proof]
		We must determine $c_1(X)=d\cdot g_2$, where $g_2$ is the positive generator of $H^2(X;\Z)$. The Chern number $c_1c_4[X]$ is fixed by $h^{p,q}(X)=$ $h^{p,q}(\CP^5)$, hence $c_1c_4[X]=90$. Thus, $d$ divides $90$. Every possibility except $d=3$ is ruled out case-by-case.\pause
	
		\bigskip
		
		Once $c_1(X)$ is fixed, Mukai's classification of Fano manifolds of coindex $3$ finishes the proof.	
	\end{myproof}
\end{frame}

\begin{frame}{The twistor space: Invariant almost complex structures}
	The second invariant almost complex structure is obtained by ``flipping the fiber''. The Chern numbers are (compare GNO~\cite{GNO2017}):\pause
	\begin{prop}
		The Chern numbers of the two invariant almost complex structures on the twistor space are:\vspace{-0.5cm}
		\begin{table}[ht!]\centering
			\begin{tabular}{lll} \toprule
				Chern Number& $Z$		& $N$ \\ \midrule
				$c_5$ 		& $6$		& $6$ \\
				$c_1^5$ 	& $4374$	& $-18$\\
				$c_1^3c_2$	& $2106$	& $-6$\\
				$c_1^2c_3$	& $594$		& $18$\\
				$c_1c_4$	& $90$		& $18$\\
				$c_1c_2^2$	& $1014$	& $-2$\\
				$c_2c_3$	& $286$		& $6$\\ \bottomrule
			\end{tabular}
		\end{table}
	\end{prop}
\end{frame}

\begin{frame}{Reminder: $G_2$ flag manifolds}
	\begin{figure}\centering
		\begin{tikzpicture}
		\draw (-1.2,0) node{$G_2/SU(3)\cong S^6$};
		\draw (1,1.5) node{\color{red}{$G_2/U(2)_-=Q$}};
		\draw[->] (0.3,1.2) -- (-0.7,0.5) 
		node[pos=0.5, anchor=south east]{\footnotesize{$\CP^2$}};
		\draw (3,3) node{$G_2/T^2$};
		\draw[->] (2.5,2.75) -- (1.5,2)
		node[pos=0.5, anchor=south east]{\footnotesize{$\CP^1$}};
		\draw[->] (3.35,2.75) -- (4.5,2)
		node[pos=0.5, anchor=south west]{\footnotesize{$\CP^1$}};
		\draw (5.15,1.5) node{\color{red}{$G_2/U(2)_+=Z$}};
		\draw[->] (1.7,1.2) -- (2.7,0.5)
		node[pos=0.5, anchor=north east]{\footnotesize{$\CP^1$}};
		\draw[->] (4.45,1.2) -- (3.45,0.5)
		node[pos=0.5, anchor=north west]{\footnotesize{$\CP^1$}};
		\draw (3.075,0) node{$G_2/SO(4)$};
		\end{tikzpicture}
	\end{figure}
\end{frame}

\begin{frame}{The quadric}
	Notation: $G_2/U(2)_-=Q$. It is (diffeomorphic to) the complex quadric 
	\begin{equation*}
		\Bigg\{ \sum_{j=0}^6 z_j^2=0\Bigg\} \subset \CP^6
	\end{equation*}
	and inherits an $SO(7)$-invariant K\"ahler-Einstein metric from the Fubini-Study metric. \pause
	
	\bigskip
	
	On the other hand, $Q\cong \P(TS^6)\cong \P(T^*S^6)$ $\rightsquigarrow$ three invariant almost complex structures.\pause
	
	\begin{rem}
		If $S^6$ is complex, there are two non-standard complex structures on the quadric.
	\end{rem}
\end{frame}

\begin{frame}{The quadric: Invariant almost complex structures}
	In total, there are four invariant almost complex structures; the fourth is obtained from $Q$ by flipping the fiber over $S^6$.
	\begin{prop}
		The Chern numbers of the four invariant almost complex structures on the quadric are:\vspace{-0.5cm}
		\begin{table}[ht!]\centering\hspace{1cm}
			\begin{tabular}{lllll} \toprule
				Chern Number& $Q$		& $\P(TS^6)$ 	& $\P(T^*S^6)$	& $X$ \\ \midrule
				$c_5$ 		& $6$ 		& $6$ 			& $6$			& $6$\\
				$c_1^5$ 	& $6250$	& $-486$		& $486$			& $-2$\\
				$c_1^3c_2$	& $2750$ 	& $-162$		& $162$			& $2$\\
				$c_1^2c_3$	& $650$ 	& $18$ 			& $18$			& $2$\\
				$c_1c_4$	& $90$ 		& $18$ 			& $18$			& $-6$\\
				$c_1c_2^2$	& $1210$ 	& $-54$ 		& $54$			& $-2$\\
				$c_2c_3$	& $286$ 	& $6$			& $6$			& $-2$\\ \bottomrule
			\end{tabular}
		\end{table}
	\end{prop}
\end{frame}


\begin{frame}[allowframebreaks]\frametitle{References}
\printbibliography
\end{frame}
	
	
\end{document}